---
title: "Penguin Data Analysis"
author: "Raj Mishra"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Penguin Data Analysis

## Loading Data

In this section, I load the `tidyverse` and `palmerpenguins` packages and use the built-in `penguins` dataset.

```{r load-data}
library(tidyverse)
library(palmerpenguins)

data("penguins")
```

## Exploring the Data

Here, I generate a summary and structure of the `penguins` dataset to understand the variables and any missing values.

```{r explore-data}
summary(penguins)
glimpse(penguins)
```

## Visualizing the Data

This scatterplot shows the relationship between bill length and bill depth across penguin species.

```{r bill-plot}
ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm, color = species)) +
  geom_point() +
  labs(title = "Bill Length vs Bill Depth by Species",
       x = "Bill Length (mm)",
       y = "Bill Depth (mm)")
```

## Conclusion

In this analysis, I explored the Palmer Penguins dataset and visualized the relationship between physical measurements. The scatterplot highlights how species differ in bill dimensions, which is useful for species classification.
